hormones

### 2019-12-06 analysis/07_hormones.Rmd
prep for correlations with hormones and gene epxression
new illustrations, new prolactin stuff

@@

@@

```{r}
write.csv(hormones, "../results/hormones.csv", row.names = F)
```

@@

```{r}
prolactin <- read_excel("../results/Pigeon prolactin concentrations juil 2018.xlsx", sheet = 1)  %>% 
            filter(Treatment == "baseline")  %>% 
            select(ColorBands,BandNo_old, Treatment, Sex, `Prolactin ng/mL`)  %>% 
            arrange(desc(`Prolactin ng/mL`))

head(prolactin,2)
```

>>>>

```{r}
colData  <- read_csv("../metadata/00_birds.csv") %>%
  mutate(RNAseq = "RNAseq",
         bird_id = bird)  %>%
   select(-X1, -bird)
colData
```

@@

prolctin1rnaseq <- full_join(prolactin, colData)
prolctin2rnaseq <- full_join(prolactin2, colData)

prolctin1rnaseq
prolctin2rnaseq
```

@@

@@

```{r}
write.csv(hormones, "../results/hormones.csv", row.names = F)
write.csv(prolactin2, "../results/07_prolactin2.csv", row.names = F)
